From physical principles to ???

### 2016-03-16 2015CompleteDerivation/completeDerivation.tex
Adding justification for topological space

\begin{justification}
TODO: all possible states form a set. All possible set of states associated with the outcome of the process form a topology. Verify requirements on entire set, empty set, intersections and unions. Distinguishability of two elements in terms of process outcome leads to Hausdorff. Processes have countable possible outcome means base for topology must be countable, or we would have elements that are not distinguishable, therefore second countability.
\end{justification}

>>>>

\begin{justification}
We claim $\mathcal{S}$ is a set. Each state is well defined as it is physically distinguishable. The collection of all possible states form a set.

We claim $\mathcal{S}$ has a topology $\mathcal{T}$. Consider the set of all possible physical outcomes associated with all physical processes. Each possible outcome is associated with a set of states that are compatible with that outcome. Let $\mathcal{T}$ be the set of all sets associated with all physical outcomes. $\mathcal{S} \in \mathcal{T}$ and is associated with unavoidable outcomes. $\varnothing \in \mathcal{T}$ and is associated with impossible outcomes. Let $V_1, V_2 \in \mathcal{T}$. Then, by definition, there exist a process $P_1$ that admits $V_1$ as an outcome and a process $P_2$ that admits $V_2$ as an outcome. Consider the process $P$ that combines the outcomes of $P_1$ and $P_2$. This always exist physically as we can prepare the same state multiple times and let it interact with each process separately. $P$ will have a possible outcome $V$ corresponding to the case where $P_1$ gave outcome $V_1$ and $P_2$ gave outcome $V_2$. The states compatible with $V$ must be in both $V_1$ and $V_2$, that is $V = V_1 \cap V_2$. Therefore $\mathcal{T}$ is closed under intersection. Let $V_1, V_2 \in \mathcal{T}$. If they are physically distinguishable, then there exists a physical process $P$ that admits both as outcomes. Given $P$, we can always construct the process $P_0$ that combines $V_1, V_2$ into a single outcome $V$ by "forgetting" which of the two was given. The states compatible with $V$ must be in either $V_1$ or $V_2$, that is $V = V_1 \cup V_2$. Therefore $\mathcal{T}$ is closed under union. $\mathcal{T}$ is a topology by definition.

We claim that $\mathcal{S}$ is Hausdorff. Let $\mathcal{s_1}, \mathcal{s_2} \in \mathcal{S}$. As states are physically distinguishable, there must exist a physical process with two outcomes $V_1, V_2 \in \mathcal{T}$ for which $s_1 \in V_1, s_2 \in V_2, V_1 \cap V_2 = \varnothing$. $\mathcal{S}$ is Hausdorff by definition.

We claim that $\mathcal{S}$ is second countable. Consider the set of outcomes of a process. As each is identified by a finite number of digits. The set of outcomes is countable. This remains true when combining processes: the number of process we can combine is countable as so it is the number of times we can prepare the same state and the intersections of countable many sets is still countable. Consider now the set, not necessarily countable, of all processes $\mathcal{P}$ that cover the whole space (i.e. union of outcomes is the whole space). Consider now the super process $P_s$ that is the combination of all elements in $\mathcal{P}$. This represents the best possible identification of each state, as no other process can further refine the set of possibilities. As states are physically distinguishable, their best possible identification must be reachable by a physical process. $P_s$ is itself a physical process. The set of outcomes represent a basis for the topology because given the outcome of this super process we can construct the outcome of all other less refined processes.  The outcomes of $P_s$ process are countable. The topology has a countable basis. $\mathcal{S}$ is second countable by definition.

\end{justification}
